Manuscript

### 2021-01-14 Manuscript/Manuscript.Rmd
update
code: add cached results
text: finish initial manual labeling description

---
title: "Manuscript"
author: "Angelo D'Ambrosio"
date: "14/1/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, error = F, dpi = 400)
```

@@

>>>>

---
title: "Manuscript"
author: "Angelo D'Ambrosio"
date: "12/1/2021"
output:
  github_document
---

```{r Setup, include=FALSE, cache=TRUE, cache.vars='annotation_summary'}
knitr::opts_knit$set(root.dir = ifelse(basename(getwd()) == 'Manuscript', dirname(getwd()), getwd()))

print(getwd())

knitr::opts_chunk$set(
	echo = F,
	error = F,
	message = FALSE,
	warning = FALSE,
	dpi = 400
)
source('Setup.R')

annotation_summary <- summarise_annotations(annotation.folder = "Annotations", plot = F)
```

@@

```{r Results}

first_query_file <- file.path("Annotations", "Records_2020-12-11", "Records_11.12.20.xlsx")

sources_first_query <- summarise_by_source(first_query_file) %>% as.list()

first_annotation_results <- annotation_summary %>% filter(Ord == 1, str_detect(Label,'Reviewed')) %>% {
    df <- .
    df$Value %>% setNames(make.names(df$Label)) %>% as.list()
}
```

The first batch of searches, performed with the two manually curated input queries, returned `r sources_first_query$Total` unique results, specifically `r sources_first_query$Pubmed` unique results from Pubmed, `r sources_first_query$WOS` from Web of Science, and `r sources_first_query$IEEE` from IEEE.\
Of the records retrieved using the input queries, `r first_annotation_results$Reviewed` were manually labeled as relevant or not for the topic of the systematic review. Of these `r with(first_annotation_results, sprintf('%d (%s)', Reviewed.positive, percent(Reviewed.positive/Reviewed)))` were labelled as positive, and `r with(first_annotation_results, sprintf('%d (%s)', Reviewed.negative, percent(Reviewed.negative/Reviewed)))` as negative.
